A Hierarchical Bayesian Framework for Inferring the Stellar Obliquity Distribution

### 2023-05-23 src/tex/ms.tex
[showyourwork] overleaf sync

% Define document class
\documentclass[twocolumn,times,linenumbers]{aastex631}
\usepackage{showyourwork}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{physics}
\usepackage[super]{nth}
\usepackage{fontawesome}
\usepackage{hyperref}

\newcommand{\dfm}[1]{\textcolor{blue}{\textbf{From DFM:} #1}}
\newcommand{\edits}[1]{\textcolor{purple}{#1}}

\received{May 1, 2023}
\revised{}
\accepted{}

@@

\subsection{Simulated Data}\label{subsec:sim}
To investigate the performance of our hierarchical Bayesian framework, we apply it to simulated data, generated with a known ground-truth stellar obliquity distribution.
We test the following \edits{five} $\cos{\psi}$ distributions: a uniform distribution bounded between $-1$ and $1$ such that $\cos{\psi} \sim \mathcal{U}(-1,1)$, three truncated Normal distributions bounded between $-1$ and $1$, such that $\cos{\psi} \sim \mathcal{N}(0, 0.2)$, $\cos{\psi} \sim \mathcal{N}(-0.4, 0.2)$, and $\cos{\psi} \sim \mathcal{N}(0.4, 0.2)$, where the first number is the mean of the distribution and the second number is the standard deviation, \edits{and lastly, a Beta distribution such that $\cos{\psi} \sim \mathrm{Beta}(3, 6)$ with the support being extended linearly from $[0, 1]$ to $[-1, 1]$}.
For each $\cos{\psi}$ distribution, we randomly generate 200 samples of sky-projected stellar obliquity $\lambda$ and stellar inclination $i_\star$. We assume the stellar spin axis is uniformly distributed around the planetary orbital axis in the azimuthal direction and the orbital inclination is $90\degr$.
The sampled $i_\star$ and $\lambda$ here are \emph{true} values. 
To simulate the observation process, we add Gaussian noise to the \emph{true} $\lambda$ and $i_\star$, using uncertainties of $\sigma_{\lambda} = 8\degr$ and $\sigma_{i_\star} = 10\degr$, which are typical of the literature sample \cite{Albrecht22}.
Using these simulated $\lambda$ measurements and their uncertainties, we infer the $\cos{\psi}$ distribution of the sample with both $\lambda$ and $i_\star$ likelihoods or $\lambda$ likelihood only.

>>>>

% Define document class
\documentclass[twocolumn,times]{aastex631}
\usepackage{showyourwork}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{physics}
\usepackage[super]{nth}
\usepackage{fontawesome}
\usepackage{hyperref}

\newcommand{\dfm}[1]{\textcolor{blue}{\textbf{From DFM:} #1}}
\newcommand{\edits}[1]{\textcolor{black}{#1}}

@@

\subsection{Simulated Data}\label{subsec:sim}

To investigate the performance of our hierarchical Bayesian framework, we apply it to simulated data, generated with a known ground-truth stellar obliquity distribution.
We test the following \edits{five} $\cos{\psi}$ distributions: a uniform distribution bounded between $-1$ and $1$ such that $\cos{\psi} \sim \mathcal{U}(-1,1)$, three truncated Normal distributions bounded between $-1$ and $1$, such that $\cos{\psi} \sim \mathcal{N}(0, 0.2)$, $\cos{\psi} \sim \mathcal{N}(-0.4, 0.2)$, and $\cos{\psi} \sim \mathcal{N}(0.4, 0.2)$, where the first number is the mean of the distribution and the second number is the standard deviation, \edits{and lastly, a Beta distribution such that $\cos{\psi} \sim \mathrm{Beta}(3, 6)$ with the support being extended linearly from $[0, 1]$ to $[-1, 1]$}.
For each $\cos{\psi}$ distribution, we randomly generate 200 samples of sky-projected stellar obliquity $\lambda$ and stellar inclination $i_\star$. We assume the stellar spin axis is uniformly distributed around the planetary orbital axis in the azimuthal direction and the orbital inclination is $90\degr$.
The sampled $i_\star$ and $\lambda$ here are \emph{true} values. 
To simulate the observation process, we add Gaussian noise to the \emph{true} $\lambda$ and $i_\star$, using uncertainties of $\sigma_{\lambda} = 8\degr$ and $\sigma_{i_\star} = 10\degr$, which are typical of the literature sample \cite{Albrecht22}.
Using these simulated $\lambda$ measurements and their uncertainties, we infer the $\cos{\psi}$ distribution of the sample with both $\lambda$ and $i_\star$ likelihoods or $\lambda$ likelihood only.
